---
title: "Composite Reference"
description: |
  Data-informed decision making in the face of crisis.
author:
  - name: Jason Jones
    url: https://www.sog.unc.edu/about/faculty-and-staff/jason-jones
    affiliation: ncIMPACT Initiative
    affiliation_url: https://ncimpact.sog.unc.edu/
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE)

library(tidyverse)
library(gt)

dat <- read_csv("data/layers.csv")
```

# Composite Background

Based on our engagement and research, we propose a three tiered approach which includes:

1.  Developing an understanding of a community's resilience and/or disposition towards widening inequity using publicly available Census data at the Census Tract level.

2.  Developing an understanding, where data is available, of the emergency financial support resources received which may be masking short-term consequences and delaying second-order impacts of the pandemic at the county level.

3.  Developing an understanding of real-time fluctuations in a selection of publicly available indicators at the county level.

We propose the combination of publicly available data to understand where economic growth and recovery may be most challenging and where communities may be at the greatest risk of the disproportionate impact of COVID-19 and widening inequities. This composite approach acknowledges the complex operating context for local government and the intricate social fabric in communities that makes it almost impossible to adopt a one-size-fits-all understanding.

The selection of indicators we propose is not intended to be comprehensive and we also do not assume that this will be the proper mix for every jurisdiction. We encourage you to be flexible within these categories and pursue indicators within each that may more adequately conform to your local context.

# Community Resilience

Developing an understanding of a community's resilience and/or disposition towards widening inequity using publicly available Census data at the Census Tract level.

```{r}
dat %>%
  filter(layer == "three") %>%
  select(title, steward) %>%
  gt() %>%
  cols_label(title = "Metric", steward = "Data Steward") %>%
  tab_style(style = list(cell_text(weight = "bold", align = "center"),
                         cell_borders(sides = "bottom", weight = px(3))),
            locations = list(cells_column_labels(everything()))) %>%
  tab_style(style = list(cell_text(align = "right"),
                         cell_borders(sides = "left", weight = px(3))),
            locations = cells_body(columns = vars(steward))) %>%
  cols_width(everything() ~ pct(50))
```

# Emergency Financial Support

Developing an understanding, where data is available, of the emergency financial support resources received which may be masking short-term consequences and delaying second-order impacts of the pandemic at the county level.

```{r}
dat %>%
  filter(layer == "two") %>%
  select(title, steward) %>%
  gt() %>%
  cols_label(title = "Metric", steward = "Data Steward") %>%
  tab_style(style = list(cell_text(weight = "bold", align = "center"),
                         cell_borders(sides = "bottom", weight = px(3))),
            locations = list(cells_column_labels(everything()))) %>%
  tab_style(style = list(cell_text(align = "right"),
                         cell_borders(sides = "left", weight = px(3))),
            locations = cells_body(columns = vars(steward))) %>%
  cols_width(everything() ~ pct(50))
```

# Real-Time Fluctuations

Developing an understanding of real-time fluctuations in a selection of publicly available indicators at the county level.

```{r}
dat %>%
  filter(layer == "one") %>%
  select(title, steward) %>%
  gt() %>%
  cols_label(title = "Metric", steward = "Data Steward") %>%
  tab_style(style = list(cell_text(weight = "bold", align = "center"),
                         cell_borders(sides = "bottom", weight = px(3))),
            locations = list(cells_column_labels(everything()))) %>%
  tab_style(style = list(cell_text(align = "right"),
                         cell_borders(sides = "left", weight = px(3))),
            locations = cells_body(columns = vars(steward))) %>%
  cols_width(everything() ~ pct(50))
```

# Aggregate Composites

\<\<Insert composite visuals and explanations\>\>
